\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-18 draft.tex
with fullpage and times on

%\usepackage{latexsym}
\usepackage{setspace}
\usepackage{cancel}
\usepackage{graphicx}
\usepackage{appendix}
\usepackage{amssymb}
\usepackage{times}
%\usepackage{cancel}
%\usepackage{verbatim}
%\usepackage{chngpage}
%\usepackage{xcolor}
%\usepackage{mathrsfs}

@@

\begin{figure}[h]

	\scalebox{0.9}{
		\begin{tikzpicture}

@@

We explain why that the validity of Equation~(\ref{eq:commu}) is sufficient to prove the commutativity of the reducer $s_1;\rloop\{s_2\};s_3$. Notice that $s_1$ does not read from the input (assumed at the beginning of this subsection). The execution of $s_1$ is deterministic in the sense that from the same initial valuation, it outputs the same sequence of values and ends at the same valuation. For the execution of $\rloop\{s_2\}$, from the validity of Equation~(\ref{eq:commu}), any permutation of input values leads the reducer to the same final valuation and the same sequence of outputs at the end of the loop.
Before executing the commands $s_3$, all inputs have been read (the loop exit condition) already. Similar to the case of $s_1$, $s_3$ does not read from the input and hence the execution of $s_3$ is deterministic. It follows that for all permutations of inputs, the reducer outputs the same sequence of values.

@@

For the general case, we first rewrite the $s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ to the form
$s'_0;x_{i_1}{:=} \cur;s'_1.\ldots x_{i_{m}}{:=}\cur;s'_m$, where $\cur$ never occur in $s'_0,s'_1,\ldots, s'_m$. Then we produce the reducer in Figure~\ref{fig:general_program_transformation}, which is an over-approximation of the original reducer for the same reason: the case that $s=1$ has the same output sequence to the original reducer and when $s\neq 1$, it may produce additional behavior. Observe that the reducer in Figure~\ref{fig:general_program_transformation} satisfies all assumptions required for the Prover. Hence the Equation~(\ref{eq:commu}) can then be applied to prove its commutativity.

>>>>

%\usepackage{latexsym}
\usepackage{setspace}
\usepackage{cancel}
\usepackage{graphicx}
\usepackage{appendix}
\usepackage{amssymb}
\usepackage{times}
\usepackage{fullpage}

%\usepackage{cancel}
%\usepackage{verbatim}
%\usepackage{chngpage}
%\usepackage{xcolor}
%\usepackage{mathrsfs}

@@

\begin{figure}[h]
\centering
	\scalebox{0.9}{
		\begin{tikzpicture}

@@

We explain why that the validity of Equation~(\ref{eq:commu}) is sufficient to prove the reducer $s_1;\rloop\{s_2\};s_3$ commutative. Notice that $s_1$ does not read from the input (assumed at the beginning of this subsection). The execution of $s_1$ is deterministic in the sense that from the same initial valuation, it outputs the same sequence of values and ends at the same valuation. For the execution of $\rloop\{s_2\}$, from the validity of Equation~(\ref{eq:commu}), any permutation of input values leads the reducer to the same final valuation and the same sequence of outputs at the end of the loop.
Before executing the commands $s_3$, all inputs have been read (the loop exit condition) already. Similar to the case of $s_1$, $s_3$ does not read from the input and hence the execution of $s_3$ is deterministic. It follows that for all permutations of inputs, the reducer outputs the same sequence of values.

@@

For the general case, we first rewrite the $s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ to the form
$$s'_0;x_{i_1}{:=} \cur;s'_1.\ldots x_{i_{m}}{:=}\cur;s'_m$$, where $\cur$ never occur in $s'_0,s'_1,\ldots, s'_m$. Then we produce the reducer in Figure~\ref{fig:general_program_transformation}, which is an over-approximation of the original reducer for the same reason: the case that $s=1$ has the same output sequence to the original reducer and when $s\neq 1$, it may produce additional behavior. Observe that the reducer in Figure~\ref{fig:general_program_transformation} satisfies all assumptions required for the Prover. Hence the Equation~(\ref{eq:commu}) can then be applied to prove its commutativity.
